\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{url}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{upgreek}
\usepackage{bm}
\usepackage{listings}
\usepackage{tikz}

\lstset{ 
  language=Python,
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{xcolor}; should come as last argument
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code 
  keywordstyle=\color{blue},       % keyword style
}

\usetikzlibrary{arrows, arrows.meta}

\bibliographystyle{plain} % We choose the "plain" reference style

\newcommand{\nn}{\nonumber}
\newcommand{\captionfont}{\tiny}
\newcommand{\QtwoQone}{$Q_2\times Q_1$}
\newcommand{\python}{\color{darkgray} \sffamily }
\newcommand{\K}{{\mathbb{K}}}
\newcommand{\G}{{\mathbb{G}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{FLAPS \\ the FLexible Axisymmetric Planet Solver}
\author{C. Thieulot}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{The physics}

%----------------------------------------------------------
\subsection{Axisymmetric formulation}
\input{axisymmetry}

%----------------------------------------------------------
\subsection{Dynamic topography}
\input{dynamic_topography}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Numerical methods}

%----------------------------------------------------------
\subsection{Finite elements}

%----------------------------------------------------------
\subsection{Mapping}
\input{mapping}

%----------------------------------------------------------
\subsection{Quadrature}



%----------------------------------------------------------
\subsection{Computing normals}

%----------------------------------------------------------
\subsection{Free slip}
\input{free_slip}

%----------------------------------------------------------
\subsection{Pressure normalisation}
\input{pressure_normalisation}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{The data}

%----------------------------------------------------------
\subsection{Earth}
\input{data_earth}

%----------------------------------------------------------
\subsection{Mars}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Benchmarking}



The goal here is to explore the influence of the mapping polynomial order and/or
the number of quadrature points on the accuracy of the solution of various benchmarks and test cases.

Concretely, in this section we will explore the effect of:
\begin{itemize}
\item resolution via the number of elements in the radial direction: {\python nelr=2-32} (we automatically set {\python nelt=12*nelr})
\item the number of quadrature points per dimension: {\python nqperdim=2,3,4,5}
\item the polynomial order of the mapping: {\python mapping='Q1','Q2','Q3','Q4'}
\end{itemize}
and we will monitor the computed area/volume, the root mean square velocity and the velocity and pressure errors.

\subsection{Computing volume/mass}


\subsection{Annulus convection manufactured solution}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The '4D dynamic earth' inter-code benchmark}

\cite{krhb12}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\appendix
\section{Misc}

%----------------------------------------------------------
\subsection{Notes to self}

What I have tried to cure the pb of the weird anomalies at the poles.

\begin{itemize}
\item turning elements into real trapezes. Made things worse
\item different mappings. not much difference
\item when using blob, reduced densities. no difference
\item nb of quad points, no real difference
\item nb of elements in tangential direction, some difference but no cure 
\item when using blob, drho/rho, no diff 
\item type of b.c. at point corner below poles, no real diff 
\item scaling of G matrix
\item different rotations/bc for free slip, no difference
\item using cmat matrix for dev strain rate, helped a little bit, no cure 
\end{itemize}



%----------------------------------------------------------
\subsection{To do list}
\begin{itemize}
\item visc profiles
\item rho profiles
\item time stepping
\item gravity calculations. import from f96, re-benchmark
\item CBF? 
\item compute self gravity for reduced density case 
\item export exx1 and exx3 to outside function, clean their code too? 
\item remove call to math 
\item bottom free slip 
\item change y for z in stone
\item use PREM gravity value
\item aspect with GMG ?
\item compute moment of inertia
\item by default code now uses elemental rho and eta. it changes things wrt exp0 benchmark results!
\end{itemize}




\bibliography{bibliography} 

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
